Post CMOS technologies: An Overview and Analysis

### 2025-05-28 Paper.tex
new text

\subsection{Introduction to Spintronics}
Spintronics is the study and exploitation of the spin 
of electrons in solid-state devices. Unlike charge, which is a 
scalar quantity, spin is a quantum mechanical property that can 
be oriented in different directions (e.g., "spin-up" or "spin-down").
This allows for the encoding of information in a non-volatile magnetic
state. The promise of spintronics lies in its ability to enable 
novel functionalities and overcome the inherent energy dissipation 
associated with moving charges in conventional electronics. By manipulating 
spin currents and magnetic states, spintronic devices aim to perform logic 
operations with significantly reduced energy footprints.

\subsection{Magnetoelectric Spin-Orbit (MESO) Devices}

>>>>

\subsection{Introduction to Spintronics}
Spintronics is the study and exploitation of the spin 
of electrons in solid-state devices. Unlike charge, which is a 
scalar quantity, spin is a quantum mechanical property that can 
be oriented in different directions (e.g., "spin-up" or "spin-down").
This allows for the encoding of information in a non-volatile magnetic
state. The promise of spintronics lies in its ability to enable 
novel functionalities and overcome the inherent energy dissipation 
associated with moving charges in conventional electronics. By manipulating 
spin currents and magnetic states, spintronic devices aim to perform logic 
operations with significantly reduced energy footprints. 
By also utilizing using a charge as well as spin this gives the potential to encode more 
states where there can be a combination of high or low voltage along 
with up or down spin.

\subsection{Magnetoelectric Spin-Orbit (MESO) Devices} 
One promising way to compute and perform logic using spintronics is 
Magnetoelectric Spin-Orbit (MESO). In this scheme binary is represented 
in the up or down spin state of a nanomagnet. These devices rely 
on 2 major physical effects. The first is spin-orbit transduction where 
if a current flows through a material with a strongly coupled spin 
the current will also gain that spin. The second effect is magnetoelectric 
switching where you can control a materials magnetic properties by applying 
an electric field. For instance switching the spin state with the help of 
an electric field.

\subsubsection{Principle of Operation}
An input logic is provided through a voltage and electric field which 
will set the magnetization in a magnet to be in a certain direction. This 
converts an electrical input into a magnetic state where the spin state 
can now be used to represent the binary 0 or 1.

To then generate an output a current is injected into the nanomagnet 
which will cause the output current from the nanomagnet to all have 
the same
